Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-15 csf-2017/paper.tex
Replace the term "stack and return pointer discipline" by "calling convention" and start shortening.

\begin{abstract}  
  Capability machines provide security guarantees at machine level
  which makes them an interesting target for compilation schemes that aim to
  provably enforce control-flow correctness, encapsulation of local
  state, and such properties.
  We provide a formalisation of a representative capability machine
  and propose a novel stack management discipline for enforcing
  control-flow correctness and encapsulation of local state on it. To prove
  these properties, we provide a logical relation that semantically
  captures capability safety. The capability safety defined by the
  logical relation goes beyond the
  proposed stack management discipline and can be used to reason about
  any capability safe program.
\end{abstract}

@@

In this paper, we make progress towards the goal of efficient and provably
watertight enforcement of encapsulation and control-flow correctness on
capability machines. Specifically, we make the following contributions:
\begin{itemize}
\item In Section~\ref{sec:capab-mach-with}, we formalise a simple but representative capability machine featuring
  local capabilities much like CHERI's, and define its operational semantics.
\item We define a novel stack management discipline for enforcing control-flow
  correctness and encapsulation of local state on the stack in
  Section~\ref{sec:stack-and-return-pointer}. The discipline relies solely on
  local capabilities (used to represent stack and return pointers) and does not
  require OS support in the form of a trusted shadow stack or special call and
  return instructions. It also does not require separate per-component stacks
  and instead works with a single, fairly standard, contiguous stack. It
  supports higher-order cross-component calls (e.g., (potentially)
  cross-component function pointers) and can be efficient assuming only one
  additional piece of processor support: an instruction for efficiently clearing
  a range of memory.
\item We provide a theorem that is (by far) the most general
  and powerful formulation of the guarantees offered by a capability machine.
  The theorem also expresses the specific guarantees offered by the machine for
  local capabilities. It is very general and not tied to a specific ABI or a
  specific way of using the system's capabilities.
\item The above theorem is formulated in terms of a unary step-indexed
  logical relation with recursively defined Kripke worlds. It is
  inspired by one used in \cite{Devriese:2016ObjCap} for
  capability safety in a JavaScript-like lambda calculus, but has two
  novel technical characteristics. The natural CPS style of assembly
  code with return pointers as continuations is modeled using a
  \emph{single} orthogonal closure, rather than the biorthogonal
  closure that has been previously used for lambda calculi. Perhaps
  more surprisingly, we show that the special nature of local
  capabilities can be elegantly expressed using a variant of an idea
  that has been used by Dreyer et. al.~\cite{Dreyer:jfp12} to express
  well-bracketedness guarantees in a lambda calculus: Kripke worlds
  with both a public and a private future world relation. Interestingly,
  the two future world relations generally work very similarly to
  Dreyer et al.'s, except that they turn up in quite a different place
  in the logical relation. The logical relation and theorem is presented in Section~\ref{sec:logical-relation}.
\item We demonstrate the power of our results in Section~\ref{sec:examples} by applying them to challenging
  examples, specifically constructed to demonstrate local state encapsulation
  and control-flow correctness guarantees in the presence of cross-component
  function pointers. The examples demonstrate both the power of our formulation
  of capability safety and our stack management discipline.
\end{itemize}
%\lau{I have left out the discussion/future work, related work and conclussion sections from the outline given with the contribution. Do you feel like there should be a dedicated outline instead and if not should we mention the last sections (I don't feel it contributes anything to mention them).}

@@

\section{A capability machine with local capabilities}
\label{sec:capab-mach-with}
In this paper, we work with a formal capability machine that has all the
characteristics of real capability machines, as well as local capabilities much
like CHERI's, but is otherwise kept as simple as possible. It is inspired by
both the M-Machine~\cite{Carter:1994:HSF:195473.195579} and
CHERI~\cite{Watson2015Cheri}. To avoid getting bogged down in uninteresting
detail, we assume an infinite address space and unbounded integers.

@@

\section{Stack and return pointer management using local capabilities}
\label{sec:stack-and-return-pointer}
%\lau{Do we want to use the term ``pointer'' at any point? I have also used it, but I guess it might create some confusing to whether we have traditional pointer as well as capabilities?}
One of the contributions in this paper is a demonstration that local
capabilities on a capability machine can be used in a stack and return pointer
management scheme that enforces control-flow correctness in a way that is provably
watertight, potentially efficient, does not rely on a trusted central stack
manager, and with support for exposing higher-order interfaces to an adversary.
In this section, we explain this discipline. We start by explaining the
high-level approach, the different issues that need to be taken into account,
starting with first-order interfaces and moving onto a higher-order setting
next. After that, we define a number of reusable macro-instructions that
can be used to conveniently apply the proposed discipline in subsequent
examples.

@@

However, if we are returning from a function that has itself invoked adversary
code, then even the unused part of the stack may still contain data and
capabilities left there by them, including local capabilities since the stack is
store-local. The adversary could take advantage of this by using the unused part
of the stack to store either stack pointers or return pointers from such
previous invocations and then use them when they're no longer supposed to. To
prevent this, before returning, we need to clear (i.e.\ overwrite with zeros) the
entire part of the stack that the adversary has had access to, not just the
parts that we have used ourselves. Essentially, this is needed for the same
reason that we clear the register file: because the adversary should not be able
to keep hold of local capabilities when control is passed to the trusted code
and back to the adversary. Clearing the entire unused part of the stack is the
most problematic aspect of our discipline in terms of efficiency, since it may
consist of a large part of memory. However, we believe there are ways to
optimize it that we discuss in Section~\ref{sec:discussion}.

@@

The final question that remains is: where should we store this activation
record? The attentive reader may already see that there is only one possibility:
since the activation record contains the old stack pointer, which is necessarily
local, the activation record can only be constructed in a part of memory where
we have write-local access, i.e.\ on the stack. Note that this means we will be
placing and executing instructions on the stack, i.e.\ it will not just contain
code pointers and data. This means that our discipline should be combined with
protection against stack smashing attacks (i.e.\ buffer overflows on the stack
overwriting activation records' contents), but conveniently, the fine-grained
memory protection on capability machines is well-suited to easily provide such
protection.

@@

\textbf{Stack management discipline}
The precautions the needed to safely interact with an adversary have now been introduced and motivated. The stack discipline comprises the precautions. Summarized, they were:
\begin{description}[font=\normalfont\itshape]
\item[At program startup] a local $\rwlx$-capability (the stack pointer) resides in register $r_\stk$. The system does not hand out global write-local capabilities.
\item[Before returning to the adversary] clear the registers (with words we do not want to pass to the adversary) and erase any part of the stack we have used (any part of the stack that has been passed to an adversary must also be erased).
\item[Before invoking the adversary] push an activation record to the stack, create a local $\entry$-capability for the restore instructions of the activation record (the return pointer) and leave it in a register, leave a copy of the stack capability restricted to the unused part in $r_\stk$, erase the part of the stack we release control over, and clear the non-argument registers.
\item[Before invoking an adversary callback] make sure it is a global capability.
\item[When called by an adversary] make sure the alleged stack pointer has permission $\rwlx$.
\end{description}
\textbf{Reusable macro instructions} 
We define a number of reusable macros. The macros capture the stack
management discipline and other conveniences. The macros are:
\texttt{\footnotesize{fetch $r$ $\var{name}$}} fetches the capability related to
$\var{name}$ from the linking table and stores it in register
$r$. \texttt{\footnotesize{push $r$}}/\texttt{\footnotesize{pop $r$}} works as one would expect. All
macros that uses the stack assumes a stack pointer in register
$r_\stk$.  \texttt{\footnotesize{prepstk $r$}} is used when a callback is invoked by
the adversary and prepares the received stack pointer by checking that
it has permission $\rwlx$ and making it conform to our stack
discipline. \texttt{\footnotesize{scall $r$($\overline{r_{\var{args}}}$,$\overline{r_{\var{priv}}}$)}} Jumps
to the capability in register $r$ in the manner described above. That
is, it pushes local state (the contents of registers
$\overline{r_{\var{priv}}}$), stack pointer and return pointer to the
stack, sets up the necessary on stack return code and creates a return
pointer, restricts the stack pointer, clears the unused part of the
stack, clears the necessary registers and jumps to $r$. Upon return,
the private state is restored. \texttt{\footnotesize{mclear $r$}} clears all the
memory the capability in register $r$ has authority
over. \texttt{\footnotesize{rclear $\var{regSet}$}} clears all the registers in
$\var{regSet}$. \texttt{\footnotesize{reqglob $r$}} checks whether the word in
register $r$ is a global capability. \texttt{\footnotesize{crtcls
  $\overline{(x_i,r_i)}$ $r$}} allocates a closure pair where the
capability in register $r$ is used to point to the program and a new
environment is allocated (using malloc) where the contents of
$\overline{r_i}$ is stored. In the program referred to by $r$, an
implicit fetch happens when an instruction refers to $x_i$.

@@

The final example, \texttt{\footnotesize{g1}} with \texttt{\footnotesize{f4}}, is a faithful translation
of a tricky example known from the
literature~\citep{pitts_operational_1998,Dreyer:jfp12}. It consists of two
parts, \texttt{\footnotesize{g1}} and \texttt{\footnotesize{f4}}. \texttt{\footnotesize{g1}} is a closure generator that
generates closures with one variable $x$ set to $0$ in its environment and
\texttt{\footnotesize{f4}} as the program. \texttt{\footnotesize{f4}} expects one argument, a callback. The
program sets $x$ to $0$ and calls the callback. When it returns, \texttt{\footnotesize{f4}}
sets $x$ to $1$ and calls the callback a second time. When it returns from the
callback, it asserts that $x$ is $1$ and returns. This example is more
complicated than the previous ones because it involves a closure invoked by the
adversary and an adversary callback invoked by us. As explained in
Section~\ref{sec:stack-and-return-pointer}, this means we need to (1) take care
to properly check the stack pointer received by our closure from the adversary
(it must have the correct permission and fit with our stack discipline) and (2)
require that the adversary callback is global.

To illustrate how subtle this program is, consider how an adversary could try to
make the assertion fail. In the second callback an adversary can get to the
first callback by invoking the closure one more time. If there were any way for
the adversary to transfer the return pointer from the point where it reinvokes
the closure to where the closure reinvokes the callback, then the assertion can
be made to fail. Similarly, if there were any way for the adversary to store a
stack pointer or trick the trusted code into preserving it across an invocation,
the assertion can likely be made to fail too. However, our stack and return
pointer discipline guarantees that there is no way any of this can happen, as we
prove in the following lemma.

@@

\subsection{Stack and return pointer discipline}
\textbf{Formulating control flow correctness} The attentive reader may notice
that, while we claim that our stack and return pointer discipline enforces
control-flow correctness, we do not prove a general theorem to show that this is
the case. The reason for this is that it is not clear what such a theorem should
look like. Formulations in terms of a control-flow graph, like the one by
\cite{abadi_control-flow_2005}, do not take into account temporal properties,
like the well-bracketedness that Example~\texttt{\footnotesize{g1}} relies on. In fact, our
examples show that our logical relation imply a form of control-flow correctness
that is stronger than such formulations, although this is not made very
explicit. As future work, we are considering to look at a more explicit and
useful way to formalise well-bracketed control flow. The idea would be to define
a variant of our capability machine with built-in call and return instructions
and well-bracketed control flow built-in to the operational semantics, and then
prove that compiling such code to our machine using our stack and return pointer
discipline is fully abstract~\cite{abadi_protection_1998}, which roughly means
that the lower-level machine does not allow interactions with the compiled code
that do not correspond to an interaction with the original code in the
high-level machine.

\textbf{Performance and the requirement for stack clearing} It is important to
consider the performance of our proposed stack and return management discipline.
Generally, the additional security measures described in
Section~\ref{sec:stack-and-return-pointer} obviously impose an overhead w.r.t.
an approach that does not provide security. However, they generally consist of a
few checks or register clearings on every boundary crossing between trusted code
and adversary, which should impose an acceptable performance overhead. The only
exception is the requirements that we have for stack clearing, in two
situations: when returning to the adversary and when invoking an adversary
callback. As we have explained, it is not sufficient to clear just the part of
the stack that we have used ourselves, but we need to clear the entire stack,
except the part that we are using ourselves. This means that on every crossing
of the boundary between trusted and adversary code, a potentially large region
of memory needs to be zeroed out entirely. We believe that this in fact is a
common requirement for typical usage scenario's of local capabilities and
capability machines like CHERI should consider to provide special support for
this requirement, in the form of a highly-optimized instruction for zeroing out
a potentially large block of memory. We have no experience in processor design,
but we imagine this might be optimized as a vector instruction or even further,
by having the processor keep track of a range of memory for which loads should
pretend that it has already been cleared, by returning zero irrespective of the
actual contents of the memory.

\textbf{Modularity} An important aspect of our stack and return pointer
discipline is that it is modular. By that, we mean that the requirements we have
on callbacks, return pointers etc. provided to trusted code by an adversary are
also satisfied by callbacks, return pointers etc. that we construct ourselves.
For example, our return pointers are necessarily local capabilities because they
must point to memory where we can store the old stack pointer, but the
adversary's return pointers are also allowed to be local. Adversary callbacks on
the other hand are required to be global but the callbacks we construct
ourselves are also allocated on the heap and global. In other words, we do not
assume that our code has some sort of special status and it is possible for the
adversary to protect themselves against us in the same way as we protect against
them.

@@

%\section{Conclusion}
\label{sec:conclusion}
\todo[inline]{Insert the correct URL for the technical report in the bibtex file!}
\begin{comment}
\section*{Acknowledgements}
\label{sec:acknowledgements}

This research was supported in part by the ModuRes Sapere Aude Advanced Grant from The Danish Council for Independent Research for the Natural Sciences (FNU).
Dominique Devriese holds a postdoctoral fellowship from the Research Foundation - Flanders (FWO).
\end{comment}
%\bibliographystyle{IEEEtran}
\bibliographystyle{plainnat}
\bibliography{IEEEabrv,references}

>>>>

\begin{abstract}  
  Capability machines provide security guarantees at machine level which makes
  them an interesting target for compilation schemes that aim to provably
  enforce properties like control-flow correctness, encapsulation of local
  state. We provide a formalisation of a representative capability machine and
  propose a novel calling convention for enforcing control-flow correctness and
  encapsulation of local state on it. To prove these properties, we provide a
  logical relation that semantically captures the guarantees provided by the
  hardware (a form of capability safety). These results are not tied to our
  calling convention and can be used to reason about arbitrary programs.
\end{abstract}

@@

In this paper, we make progress towards the goal of efficient and provably
watertight enforcement of encapsulation and control-flow correctness on
capability machines. Specifically, we make the following contributions:
\begin{itemize}
\item Formalise a simple but representative capability machine featuring local
  capabilities, and its operational semantics
  (Section~\ref{sec:capab-mach-with})
\item Define a novel calling convention enforcing control-flow correctness and
  encapsulation of local state on the stack
  (Section~\ref{sec:stack-and-return-pointer}). It relies solely on local
  capabilities and does not require OS support (like a trusted stack or
  call/return instructions). It also does not use separate per-component stacks
  but a single, fairly standard, contiguous stack. It supports higher-order
  cross-component calls (e.g., (potentially) cross-component function pointers)
  and can be efficient assuming only one additional piece of processor support:
  an efficient instruction for clearing a memory range.
\item Prove a theorem that is the most general and powerful formulation of the
  guarantees offered by a capability machine (a form of capability
  safety~\cite{Devriese:2016ObjCap,Maffeis2010OC}), including the specific
  guarantees offered for local capabilities. It is very general and not tied to
  our calling convention or a specific way of using the system's capabilities.
\item Introduce two novel technical ideas in the unary, step-indexed Kripke
  logical relation used to formulate the above theorem. First, we model the
  naturally continuation-passing-style of assembly code (with return pointers as
  continuations) using a \emph{single} orthogonal closure, rather than the
  existing biorthogonal closure. Secondly, we express the special nature of
  local capabilities using a variant of Dreyer et. al.'s public and private
  future worlds~\citep{Dreyer:jfp12}, used to express well-bracketedness
  guarantees in a lambda calculus. The logical relation and capability safety
  theorem is presented in Section~\ref{sec:logical-relation}.
\item Demonstrate our results by applying them to challenging examples,
  specifically constructed to demonstrate local state encapsulation and
  control-flow correctness guarantees in the presence of cross-component
  function pointers (Section~\ref{sec:examples}). The examples demonstrate both
  the power of our formulation of capability safety and our calling convention.
\end{itemize}
%\lau{I have left out the discussion/future work, related work and conclussion sections from the outline given with the contribution. Do you feel like there should be a dedicated outline instead and if not should we mention the last sections (I don't feel it contributes anything to mention them).}

@@

\section{A capability machine with local capabilities}
\label{sec:capab-mach-with}
In this paper, we work with a formal capability machine with all the
characteristics of real capability machines, as well as local capabilities much
like CHERI's. Otherwise, it is kept as simple as possible. It is inspired by
both the M-Machine~\cite{Carter:1994:HSF:195473.195579} and
CHERI~\cite{Watson2015Cheri}. To avoid uninteresting detail, we assume an
infinite address space and unbounded integers.

@@

\section{Stack and return pointer management using local capabilities}
\label{sec:stack-and-return-pointer}
%\lau{Do we want to use the term ``pointer'' at any point? I have also used it, but I guess it might create some confusing to whether we have traditional pointer as well as capabilities?}
One of the contributions in this paper is a demonstration that local
capabilities on a capability machine can be used in a calling convention that
enforces control-flow correctness in a way that is provably watertight,
potentially efficient, does not rely on a trusted central stack manager, and
with support for exposing higher-order interfaces to an adversary. In this
section, we explain this convention. We start by explaining the high-level
approach, the different issues that need to be taken into account, starting with
first-order interfaces and moving onto a higher-order setting next. After that,
we define a number of reusable macro-instructions that can be used to
conveniently apply the proposed convention in subsequent examples.

@@

However, if we are returning from a function that has itself invoked adversary
code, then even the unused part of the stack may still contain data and
capabilities left there by them, including local capabilities since the stack is
store-local. The adversary could take advantage of this by using the unused part
of the stack to store either stack pointers or return pointers from such
previous invocations and then use them when they're no longer supposed to. To
prevent this, before returning, we need to clear (i.e.\ overwrite with zeros)
the entire part of the stack that the adversary has had access to, not just the
parts that we have used ourselves. Essentially, this is needed for the same
reason that we clear the register file: because the adversary should not be able
to keep hold of local capabilities when control is passed to the trusted code
and back to the adversary. Clearing the entire unused part of the stack is the
most problematic aspect of our calling convention in terms of efficiency, since
it may consist of a large part of memory (but see Section~\ref{sec:discussion}
for how this might be mitigated).

@@

The final question that remains is: where should we store this activation
record? The attentive reader may already see that there is only one possibility:
since the activation record contains the old stack pointer, which is necessarily
local, the activation record can only be constructed in a part of memory where
we have write-local access, i.e.\ on the stack. Note that this means we will be
placing and executing instructions on the stack, i.e.\ it will not just contain
code pointers and data. This means that our calling convention should be
combined with protection against stack smashing attacks (i.e.\ buffer overflows
on the stack overwriting activation records' contents), but conveniently, the
fine-grained memory protection on capability machines is well-suited to easily
provide such protection.

@@

\textbf{Calling convention} With the security measures introduced and motivated,
here is a summary of our proposed calling convention:
\begin{description}[font=\normalfont\itshape]
\item[At program startup] a local $\rwlx$-capability (the stack pointer) resides in register $r_\stk$. The system never hands out global write-local capabilities.
\item[Before returning to the adversary] clear the non-return-value registers and the entire part of the stack that we had access to.
\item[Before invoking the adversary] push an activation record to the stack, create a return pointer as a local $\entry$-capability to the instructions in the activation record, restrict the stack capability to the unused part in $r_\stk$, clear that part of the stack, and clear the non-argument registers.
\item[Before invoking an adversary callback] make sure the callback capability is global.
\item[When called by an adversary] make sure the received stack pointer has permission $\rwlx$.
\end{description}
\textbf{Reusable macro instructions} 
We define a number of reusable macros capturing the calling convention and other conveniences. The macros are:
\texttt{\footnotesize{fetch $r$ $\var{name}$}} fetches the capability related to
$\var{name}$ from the linking table and stores it in register
$r$. \texttt{\footnotesize{push $r$}}/\texttt{\footnotesize{pop $r$}} works as one would expect. All
macros that uses the stack assumes a stack pointer in register
$r_\stk$.  \texttt{\footnotesize{prepstk $r$}} is used when a callback is invoked by
the adversary and prepares the received stack pointer by checking that
it has permission $\rwlx$ and making it conform to our calling convention. \texttt{\footnotesize{scall $r$($\overline{r_{\var{args}}}$,$\overline{r_{\var{priv}}}$)}} Jumps
to the capability in register $r$ in the manner described above. That
is, it pushes local state (the contents of registers
$\overline{r_{\var{priv}}}$), stack pointer and return pointer to the
stack, sets up the necessary on stack return code and creates a return
pointer, restricts the stack pointer, clears the unused part of the
stack, clears the necessary registers and jumps to $r$. Upon return,
the private state is restored. \texttt{\footnotesize{mclear $r$}} clears all the
memory the capability in register $r$ has authority
over. \texttt{\footnotesize{rclear $\var{regSet}$}} clears all the registers in
$\var{regSet}$. \texttt{\footnotesize{reqglob $r$}} checks whether the word in
register $r$ is a global capability. \texttt{\footnotesize{crtcls
  $\overline{(x_i,r_i)}$ $r$}} allocates a closure pair where the
capability in register $r$ is used to point to the program and a new
environment is allocated (using malloc) where the contents of
$\overline{r_i}$ is stored. In the program referred to by $r$, an
implicit fetch happens when an instruction refers to $x_i$.

@@

The final example, \texttt{\footnotesize{g1}} with \texttt{\footnotesize{f4}}, is a faithful translation
of a tricky example known from the
literature~\citep{pitts_operational_1998,Dreyer:jfp12}. It consists of two
parts, \texttt{\footnotesize{g1}} and \texttt{\footnotesize{f4}}. \texttt{\footnotesize{g1}} is a closure generator that
generates closures with one variable $x$ set to $0$ in its environment and
\texttt{\footnotesize{f4}} as the program. \texttt{\footnotesize{f4}} expects one argument, a callback. The
program sets $x$ to $0$ and calls the callback. When it returns, \texttt{\footnotesize{f4}}
sets $x$ to $1$ and calls the callback a second time. When it returns from the
callback, it asserts that $x$ is $1$ and returns. This example is more
complicated than the previous ones because it involves a closure invoked by the
adversary and an adversary callback invoked by us. As explained in
Section~\ref{sec:stack-and-return-pointer}, this means we need to (1) take care
to properly check the stack pointer received by our closure from the adversary
(it must have the correct permission and fit with our calling convention) and (2)
require that the adversary callback is global.

To illustrate how subtle this program is, consider how an adversary could try to
make the assertion fail. In the second callback an adversary can get to the
first callback by invoking the closure one more time. If there were any way for
the adversary to transfer the return pointer from the point where it reinvokes
the closure to where the closure reinvokes the callback, then the assertion can
be made to fail. Similarly, if there were any way for the adversary to store a
stack pointer or trick the trusted code into preserving it across an invocation,
the assertion can likely be made to fail too. However, our calling convention
guarantees that there is no way any of this can happen, as we prove in the
following lemma.

@@

\subsection{Calling convention}
\textbf{Formulating control flow correctness} The attentive reader may notice
that, while we claim that our calling convention enforces control-flow
correctness, we do not prove a general theorem to show that this is the case.
The reason for this is that it is not clear what such a theorem should look
like. Formulations in terms of a control-flow graph, like the one by
\cite{abadi_control-flow_2005}, do not take into account temporal properties,
like the well-bracketedness that Example~\texttt{\footnotesize{g1}} relies on.
In fact, our examples show that our logical relation imply a form of
control-flow correctness that is stronger than such formulations, although this
is not made very explicit. As future work, we are considering to look at a more
explicit and useful way to formalise well-bracketed control flow. The idea would
be to define a variant of our capability machine with built-in call and return
instructions and well-bracketed control flow built-in to the operational
semantics, and then prove that compiling such code to our machine using our
calling convention is fully abstract~\cite{abadi_protection_1998}, which roughly
means that the lower-level machine does not allow interactions with the compiled
code that do not correspond to an interaction with the original code in the
high-level machine.

\textbf{Performance and the requirement for stack clearing} It is important to
consider the performance of our proposed calling convention.
Generally, the additional security measures described in
Section~\ref{sec:stack-and-return-pointer} obviously impose an overhead w.r.t.
an approach that does not provide security. However, they generally consist of a
few checks or register clearings on every boundary crossing between trusted code
and adversary, which should impose an acceptable performance overhead. The only
exception is the requirements that we have for stack clearing, in two
situations: when returning to the adversary and when invoking an adversary
callback. As we have explained, it is not sufficient to clear just the part of
the stack that we have used ourselves, but we need to clear the entire stack,
except the part that we are using ourselves. This means that on every crossing
of the boundary between trusted and adversary code, a potentially large region
of memory needs to be zeroed out entirely. We believe that this in fact is a
common requirement for typical usage scenario's of local capabilities and
capability machines like CHERI should consider to provide special support for
this requirement, in the form of a highly-optimized instruction for zeroing out
a potentially large block of memory. We have no experience in processor design,
but we imagine this might be optimized as a vector instruction or even further,
by having the processor keep track of a range of memory for which loads should
pretend that it has already been cleared, by returning zero irrespective of the
actual contents of the memory.

\textbf{Modularity} An important aspect of our calling convention is that it is
modular. By that, we mean that the requirements we have on callbacks, return
pointers etc. provided to trusted code by an adversary are also satisfied by
callbacks, return pointers etc. that we construct ourselves. For example, our
return pointers are necessarily local capabilities because they must point to
memory where we can store the old stack pointer, but the adversary's return
pointers are also allowed to be local. Adversary callbacks on the other hand are
required to be global but the callbacks we construct ourselves are also
allocated on the heap and global. In other words, we do not assume that our code
has some sort of special status and it is possible for the adversary to protect
themselves against us in the same way as we protect against them.

@@

%\section{Conclusion}
\label{sec:conclusion}
\todo[inline]{Insert the correct URL for the technical report in the bibtex file!}

\begin{comment}
\section*{Acknowledgements}
\label{sec:acknowledgements}

This research was supported in part by the ModuRes Sapere Aude Advanced Grant from The Danish Council for Independent Research for the Natural Sciences (FNU).
Dominique Devriese holds a postdoctoral fellowship from the Research Foundation - Flanders (FWO).
\end{comment}

%\bibliographystyle{IEEEtran}
\bibliographystyle{plainnat}
\bibliography{IEEEabrv,references}
